---
title: A Timeline of Marriages in Toronto Before and After COVID
author: 
  - Justin Klip
thanks: "Code and data are available at: https://open.toronto.ca/dataset/marriage-licence-statistics/."
date: 19 September 2024 
date-format: long
abstract: "COVID 19 has had many effects on society, one being the rate of marriage. In this paper we plot and outline the data of marriage licenses acquired in Toronto. This will demonstrate how marriage license quantity declined during COVID, and rebounded hard right after."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

We use @talia, @opendatatoronto, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

As seen in our plot here, we can see that marriages tend to follow a season pattern before COVID-19. After COVID-19, there is an uptick once again in the number of marriage licenses, and there is also much more variance month to month and the seasonal pattern seems to have disappeared.

# Discussion

## First discussion point {#sec-first-point}

Marriages are very important and interesting to study as they can represent societal trends.

## Second discussion point

## Third discussion point

## Weaknesses and next steps


\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


